%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome5}
%\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{ragged2e}
% if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.8,bottom=3pt,top=10pt]{geometry}
\usepackage{multicol}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

\newcommand{\cvdoublecolumn}[2]{%
  \cvitem[0.75em]{}{%
    \begin{minipage}[t]{\listdoubleitemcolumnwidth}#1\end{minipage}%
    \hfill%
    \begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}%
    }%
}
\newcommand{\cvreference}[5]{%
    \textbf{#1}\hfill%
    \ifthenelse{\equal{#5}{}}{}{\emailsymbol~\texttt{#5}\newline}% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{#4}%
}

% personal data
\name{Hill}{Choy}

\newcommand*{\customcvedu}[7][.25em]{
    \begin{tabular}{@{}l} 
        {\bfseries #4}
      \end{tabular}
      \hfill% move it to the right
      \begin{tabular}{l@{}}
         {\bfseries #5}
      \end{tabular} \\
      \begin{tabular}{@{}l} 
        {\itshape #3}
      \end{tabular}
      \hfill% move it to the right
      \begin{tabular}{l@{}}
         {\itshape #2}
      \end{tabular}
      \ifx&#7&%
      \else{\\%
        \begin{minipage}{\maincolumnwidth}%
          \small#7%
        \end{minipage}}\fi%
      \par\addvspace{#1}
}
  
\newcommand*{\customcventry}[5][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #3}
  \end{tabular} 
  %\begin{tabular}{@{}l} 
  %  {\itshape #1}
  %\end{tabular}
  %\hfill% move it to the right
  %\begin{tabular}{l@{}}
  %   {\itshape #2}
  %\end{tabular}
  \ifx&#5&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#5%
    \end{minipage}}\fi%
  %\par\addvspace{#1}
  }

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

\let\cleardoublepage=\clearpage

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                        
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-10mm}

\begin{center}
\begin{tabular}{ c c c c }
 \emailsymbol hill.choy.25@ucl.ac.uk & \faGithub\enspace \href{https://github.com/hillhc}{\textbf{hillhc}} & \faMobile\enspace +44 7871 067385, +852 6171 8745 & \faGlobe\enspace \href{https://hillchoy.com/}{\textbf{my website}} \\  
\end{tabular}
\end{center}

\section{SUMMARY}
Software and Computer Vision Engineer experienced in deploying end-to-end AI pipelines and building robust backend systems. Adept at translating complex Edge AI concepts into practical solutions, utilizing novel technologies to solve real-life challenges and automate physical workflows for commercial clients and local authorities.

\section{EDUCATION}
{\customcvedu{Expected Graduation: September 2026}{MSc Computer Graphics, Vision and Imaging}{University College London (UCL)}{}{}{}}
\vspace{-1mm} 
\begin{itemize}
    \item \small{\textbf{Highlighted Coursework}: Machine Vision, ML for Visual Computing, Inverse Problems, Robot Vision.}
\end{itemize}
\vspace{2mm}
{\customcvedu{Graduation: July 2024}{BEng in Computer Engineering (\textbf{Second Class Honors, Division 1})}{Hong Kong University of Science and Technology (HKUST)}{}{}{}}
\vspace{-1mm} 
\begin{itemize}
  \item \small{\textbf{Highlighted Coursework}: Intro to NLP, Computer \textbf{\&} Communication Networks.}
\end{itemize}
\vspace{2mm}
{\customcvedu{8.0 (Reading: 8.5, Listening: 9.0, Writing: 7.0, Speaking: 7.0)}{}{IELTS Academic}{}{}{}}

%\newpage
\section{RELEVANT EXPERIENCE}

\customcventry{Hyperspectral Image Analysis for Safe-Fabric Segmentation}{United Kingdom}{} 
{
  \begin{minipage}[t]{\textwidth}
    \textit{UCL, MSc Industry Dissertation Project (Partner: \textbf{Zori Tex})} \hfill \textit{Ongoing}
  \end{minipage}
}
{
  \begin{itemize}
    \item Collaborating with industry partner Zori Tex to research and develop an automated computer vision pipeline for textile waste sorting utilizing hyperspectral imaging.
    \item Exploring PCA and shallow networks to condense high-dimensional data for memory-efficient CNN processing, alongside a weakly supervised Autoencoder approach to handle uneven real-world illumination.
  \end{itemize}
}{}
\vspace{2mm} 
\customcventry{Research Assistant}{Hong Kong}{} 
{
  \begin{minipage}[t]{\textwidth}
    \textit{Prof. Shueng-Han Gary Chan, CSE, HKUST} \hfill \textit{08/2024 - 06/2025}
  \end{minipage}
}
{
  \begin{itemize}
    \vspace{1mm}
    \item \textbf{K11 MUSEA Cars and Pedestrian Flow Monitoring System}
        \begin{itemize}
            \item Engineered an end-to-end analytics system tracking 60,000+ daily visitors, utilizing OpenCV and a PyTorch-based YOLO model for real-time local flow counting on edge platforms.
            \vspace{1mm}
            \item Developed a multithreaded Flask backend utilizing Redis for real-time data synchronization and SQLite/ Pandas for robust storage, powering a web dashboard to optimize mall operations.
        \end{itemize}
    \vspace{1mm}
    \item \textbf{Privacy-Preserving Elderly Monitoring with a Novel Edge AI Camera}
        \begin{itemize}
            \item Contributed to the development of a privacy-preserving Edge AI fall-detection system deployed on an NPU-accelerated OrangePi, utilizing Human Pose Estimation for real-time patient monitoring.
            \vspace{1mm}
            \item Developed rule-based post-processing algorithms to minimize false alarms without compromising true positive cases, achieving 98\% accuracy and securing the Silver Award at the Hong Kong ICT Awards 2024.
        \end{itemize}
    \vspace{1mm}
    \item \textbf{Smart Traffic Management System (Kung Tong, Hong Kong)}
        \begin{itemize}
            \item Trained and deployed YOLO models on a dual-RTX 4090 server to process live streams from 33 cameras across 11 major junctions, monitoring 20,000+ daily vehicles per junction.
            \vspace{1mm}
            \item Engineered automated client scripts using Python requests to securely transmit vehicle counts and yellow-box stop detections to a centralized API, handling Keycloak OAuth2 token authentication.
        \end{itemize}
  \end{itemize}
}{}
\vspace{2mm} 
\customcventry{Advanced Video Analytics and Edge AI for Smart Carpark Systems}{Hong Kong}{} 
{
  \begin{minipage}[t]{\textwidth}
    \textit{HKUST, Bachelor Degree Final Year Project (Supervisor: \textbf{Prof. Shueng-Han Gary Chan, CSE, HKUST})} \hfill \textit{09/2023 - 04/2024}
  \end{minipage}
}
{
  \begin{itemize}
    \item Designed an Edge AI smart car park system to track real-time space availability, utilizing OpenCV for video frame grabbing and preprocessing to handle complex feeds from custom low-light and wide-angle cameras.
    \vspace{1mm}
    \item Deployed a PyTorch-based YOLOv8 model on a Raspberry Pi by integrating a MobileNetV3 backbone, converting to ONNX format, and utilizing Ultralytics for custom dataset annotation, halving inference latency and reducing parameters by 30\% while maintaining baseline accuracy.
  \end{itemize}
}{}
\vspace{2mm} 
\customcventry{Intern}{Hong Kong}{} 
{
  \begin{minipage}[t]{\textwidth}
    \textit{Hong Kong Telecom (HKT), Integrated Service Provision Center} \hfill \textit{06/2023 - 04/2025}
  \end{minipage}
}
{
  \begin{itemize}
    \item Engineered a Python GUI executable to replace a legacy system and eliminate manual checks, automating both Excel and physical report generation for phone line data.
    \vspace{1mm}
    \item Bypassed the lack of a native API using a custom web-scraping pipeline, dynamically extracting interface records to synchronize data with a MySQL database.
  \end{itemize}
}{}
  %-----       letter       ---------------------------------------------------------
\end{document}
%% end of file `template.tex'.